A Monte Carlo Synthetic Acceleration Method for Solving the Thermal Radiation Diffusion Equation

### 2012-07-13 doc/jcomp2012/jcomp2012.tex
Adding adjoint vs. direct convergence data and figures
Updates to the jcomp2012 paper

  \title{A Monte Carlo Synthetic Acceleration Method for Solving the
    Thermal Radiation Diffusion Equation\tnoteref{label1}}
  \tnotetext[label1]{}

@@

  \address[ornl]{Oak Ridge National Laboratory, 
    1 Bethel Valley Rd., Oak Ridge, TN 378131 U.S.A.}
  \address[wisc]{University of Wisconsin-Madison, 1500 Engineering
    Dr., Madison, WI 53716, U.S.A.}

@@

\begin{figure}[htpb!]
  \centerline{
    \input{3D_mesh_segment.pstex_t}}
  \caption{3D mesh-segment.  The particle's current cell (in blue) is
    connected to 6 adjacent cells.  The cell numbers are plotted
    alongside the mesh such that the blue cell has index 7, the high
    $z$ cell has index 2, etc.}
  \label{fig:mesh_segment}
\end{figure}

@@

@@

%%
%% End of file `elsarticle-template-num.tex'.

>>>>

  \title{A Monte Carlo Synthetic Acceleration Method for Solving the
    Thermal Radiation Diffusion Equation}

@@

  \address[ornl]{Oak Ridge National Laboratory, 
    1 Bethel Valley Rd., Oak Ridge, TN 378131 U.S.A.}
  \address[wisc]{University of Wisconsin-Madison, 1500 Engineering
    Dr., Madison, WI 53716 U.S.A.}

@@

\begin{figure}[htpb!]
  \centerline{
    \input{3D_mesh_segment.pdftex_t}}
  \caption{3D mesh-segment.  The particle's current cell (in blue) is
    connected to 6 adjacent cells.  The cell numbers are plotted
    alongside the mesh such that the blue cell has index 7, the high
    $z$ cell has index 2, etc.}
  \label{fig:mesh_segment}
\end{figure}

@@

%%---------------------------------------------------------------------------%%

@@

%%
%% End of file `jcomp2012.tex'.
